## Install

The `bbbq` package depends on the `tmhmm` package, which needs
to be installed first:

```
remotes::install_github("richelbilderbeek/tmhmm")
```

The `tmhmm` package relies on TMHMM that needs to be installed:

```
tmhmm::install_tmhmm("http://www.cbs.dtu.dk/download/D3198788-0F1D-11E9-883C-84B3B9CD16B5/")
```

The URL can be obtained by requesting a download link at 
the [TMHMM](http://www.cbs.dtu.dk/services/TMHMM) website 
at [http://www.cbs.dtu.dk/services/TMHMM](http://www.cbs.dtu.dk/services/TMHMM).
As this URL expires after four hours, `tmhmm` cannot do this for you.

The installation of NetMHC2pan is checked, with the goal of giving
a helpful error message:

```{r}
tmhmm::check_tmhmm_installation()
```

Additionall, The `bbbq` package depends on the `netmhc2pan` package, which needs
to be installed as well:

```
remotes::install_github("richelbilderbeek/netmhc2pan")
```

The `netmhc2pan` package relies on NetMHCIIpan that needs to be installed:

```
netmhc2pan::install_netmhc2pan("http://www.cbs.dtu.dk/download/33A6B0AC-0F2E-11E9-B4D1-8ABCB9CD16B5/")
```

The URL can be obtained by requesting a download link at
the [NetMHCIIpan](www.cbs.dtu.dk/services/NetMHCIIpan) website 
at [www.cbs.dtu.dk/services/NetMHCIIpan]www.cbs.dtu.dk/services/NetMHCIIpan).
As this URL expires after four hours, `netmhc2pan` cannot do this for you.

The installation of NetMHC2pan is checked, with the goal of giving
a helpful error message:

```{r}
netmhc2pan::check_netmhc2pan_installation()
```

Another dependency is the `epitopiome` package.
Installing the `epitopeome` package:

```
remotes::install_github("richelbilderbeek/epitopeome")
```

```
remotes::install_github("richelbilderbeek/bbbq")
```

