---
title: "MHC-II haplotypes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mhc2_haplotypes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(testthat)
library(bbbq)
library(netmhc2pan)
```


Greenbaum et al. [1], published the following list of MHC-II haplotype occurances:

```{r}
knitr::kable(head(bbbq::get_mhc2_haplotype_occurance()))
```

NetMHC2pan has these haplotypes:

```{r}
head(netmhc2pan::get_netmhc2pan_alleles())
```

Here we find out which NetMHC2pan haplotypes we will be using.

```{r}
df <- bbbq::get_mhc2_haplotype_occurance()
df$name <- df$haplotype
```


## References

 * [1] Greenbaum, J., Sidney, J., Chung, J., Brander, C., Peters, B. 
   & Sette, A. (2011) Functional classification of class ii human leukocyte 
  antigen (HLA) molecules reveals seven different supertypes and a surprising 
  degree of repertoire sharing across supertypes. Immunogenetics, 63, 325–335.
